MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-23 paper.Rmd
Added BibTeX version of database reference.

<!-- The forces on stars, galaxies, and dark matter under external gravitational -->
<!-- fields lead to the dynamical evolution of structures in the universe. The orbits -->
<!-- of these bodies are therefore key to understanding the formation, history, and -->
<!-- future state of galaxies. The field of "galactic dynamics," which aims to model -->
<!-- the gravitating components of galaxies to study their structure and evolution, -->
<!-- is now well-established, commonly taught, and frequently used in astronomy. -->
<!-- Aside from toy problems and demonstrations, the majority of problems require -->
<!-- efficient numerical tools, many of which require the same base code (e.g., for -->
<!-- performing numerical orbit integration). -->

@@

Historically, SEA has analyzed energy flows through specific countries
using spreadsheets, 
with data in varying and inconsistent formats 
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa].
Scientists in the field wanted to expand to cover all countries, but
the spreadsheet approach to data analysis would not scale.
We developed a series of `R` packages to enable 
analyses for all countries, as described in the following table.

>>>>

@@

Historically, SEA has analyzed energy flows through specific countries
using spreadsheets, 
with data in varying and inconsistent formats 
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa].
The authors and others in the field
wanted to expand to cover all countries, but
the spreadsheet approach to data analysis would not scale.
We developed a series of `R` packages to enable 
analyses for all countries, as described in the following table.

Reference for data repository [@Marshall:2023aa].
